Detecting Treatment-Subgroup Interactions in Clustered Data with Generalized Linear Mixed-Effects Model Trees

### 2017-05-01 pkg/glmertree/paper/treatment_interactions.Rnw
small touch-ups in abstract and intro -> tutorial already mentioned to be in vignette only
try to use "GLMM trees" (plural) or "GLMM tree algorithm" (singular) more
consistently

a few further style touch ups: Figure~\ref{} / node~X / minus in math mode



git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1294 255f4249-2263-4417-b1ea-8498779e27a7

\section{Abstract}
Identification of subgroups of patients for which treatment A is more effective than treatment B, and vice versa, is of key importance to the development of personalized medicine. Tree-based algorithms are helpful tools for the  detection of such interactions, but none of the available algorithms allow for taking into account clustered or nested dataset structures, which are particularly common in psychological research. Therefore, we propose the generalized linear mixed-effects model trees (GLMM tree) algorithm, which allows for the detection of treatment-subgroup interactions, while accounting for the clustered structure of a dataset. The algorithm uses model-based recursive partitioning to detect treatment-subgroup interactions, and a GLMM to estimate the random-effects parameters. In a short tutorial, we show how GLMM trees can be fit with the R package \verb|glmertree|. In a simulation study, GLMM tree showed higher accuracy in recovering treatment-subgroup interactions, higher predictive accuracy, and lower Type-II error rates than GLM-based recursive partitioning and mixed-effects regression trees. Also, GLMM tree showed somewhat higher predictive accuracy than linear mixed-effects model with pre-specified interaction effect, on average. We illustrate the application of GLMM tree on an individual patient-level data meta-analysis on treatments for depression. We conclude that GLMM tree is a promising exploratory tool for the detection of treatment-subgroup interactions in clustered datasets.\\
\\
\textit{Keywords}: model-based recursive partitioning, treatment-subgroup interactions, random effects, generalized linear mixed-effects model, classification and regression trees

@@

In research on the efficacy of treatments for somatic and psychological disorders, the one-size-fits-all paradigm is slowly losing ground, and personalized or stratified medicine is becoming increasingly important. Stratified medicine presents the challenge of finding which patients respond best to which treatments. This can be referred to as the detection of treatment-subgroup interactions \cite<e.g., >{DoovyDuss14}. Often, treatment-subgroup interactions are studied using linear models, such as factorial analysis of variance techniques, in which potential moderators have to be specified a-priori, have to be checked one at a time, and continuous moderator variables have to be discretized. This may hamper identification of which treatment works best for whom, especially when there are no a-priori hypotheses about treatment-subgroup interactions. As noted by \citeA{KreayFran06}, there is a need for methods that generate instead of test such hypotheses.

@@

Due to the recursive nature of the splitting, the rectangular regions of the partition can be graphically depicted as nodes in a decision tree, as shown in the example in Figure \ref{fig:exampletree}. The partition in Figure \ref{fig:exampletree} is rather simple, based on the values of two predictor variables: duration and anxiety. The resulting tree has a depth of two, as the longest path travels along two splits. Each of the splits in the tree is defined by a splitting variable and value. The first split in the tree separates the observations into two subgroups, based on the splitting variable duration and a splitting value of 8, yielding two rectangular regions, represented by node 2 and node 3. As the observations in node 2 are not further split, node 2 is a terminal node. Node 3 is an inner node, as the observations in this node are further split into nodes 4 and 5, based on the anxiety variable.

If the partition in Figure \ref{fig:exampletree} would be used for prediction of a new observation, the new observation would be assigned to one of the terminal nodes according to its values on the splitting variables. The prediction is then determined by the distribution of the training observations within the terminal node. For example, the prediction may be the node-specific mean of a single continuous variable. In the current paper, we focus on trees where the terminal nodes consist of a linear (LM) or generalized linear model (GLM), in which case the predicted value for a new observation is determined by the node-specific parameter estimates of the (G)LM.

@@

In many instances, researchers may want to detect treatment-subgroup interactions in clustered or nested datasets. For example, in individual-level patient data meta-analyses, where datasets of multiple clinical trials on the same treatments are pooled. In such analyses, the nested or clustered structure of the dataset should be taken into account by including study-specific random effects in the model, prompting the need for a mixed-effects model \cite<e.g., >{CoopyPatt09,HiggyWhit01}. In linear models, ignoring the clustered structure may lead, for example, to biased inference due to underestimated standard errors \cite<e.g., >{BrykyRaud92}. For tree-based methods, ignoring the clustered structure has been found to result in the detection of spurious subgroups and inaccurate predictor variable selection \cite<e.g., >{SelaySimo12, Mart15}. However, none of the purely tree-based methods for treatment-subgroup interaction detection allow for taking into account the clustered structure of a dataset. Therefore, in the current paper, we present a tree-based algorithm which can be used for the detection of interactions and non-linearities in GLMM type models: generalized linear mixed-effects model tree, or GLMM tree.

The GLMM tree algorithm builds on model-based recursive partitioning (MOB, \citeNP{ZeilyHoth08}), which offers a flexible framework for subgroup detection. For example, GLM-based MOB has been applied to detect treatment-subgroup interactions for the treatment of depression \cite{DrieySmit16} and amyotrophic lateral sclerosis \cite{SeibyZeil15}. In contrast to other purely tree-based methods \cite<e.g., >{ZeilyHoth08, SuyTsai09, DussyDoov16}, GLMM tree allows for taking into account the clustered structure of datasets. In contrast to previously suggested regression trees with random effects, GLMM tree allows for treatment effect estimation, with continuous as well as non-continuous response variables \cite<e.g., >{HajjyBell11,SelaySimo12}.

The remainder of this paper is structured into four sections: In the first section, we introduce the GLMM tree algorithm using an artificial motivating dataset with treatment-subgroup interactions. The second section is a short tutorial on how to fit GLMM trees using the R package \verb|glmertree|. In the third section, we compare the performance of GLMM tree with that of three other methods: MOB trees without random effects, mixed-effects regression trees (MERTs) and linear mixed-effects models with pre-specified interactions. In the fourth section, we apply GLMM tree to an existing dataset of a patient-level meta-analysis on the effects of psycho- and pharmacotherapy for depression. In the fith and last section we summarize the results and discuss limitations and directions for future research.

@@

The outcome variable was generated such that there were three subgroups with differential treatment effectiveness, corresponding to the terminal nodes in Figure \ref{fig:exampletree}: The first subgroup of patients corresponds to node~3 and shows lower post-treatment depression in Treatment~1 than in Treatment~2. The second subgroup of patients corresponds to node~4 and shows about equal post-treatment depression in both treatment conditions. The third subgroup of patients corresponds to node~5 and shows lower post-treatment depression in Treatment~2 than in Treatment~1. Thus, duration and anxiety are true partitioning or moderator variables, whereas age is not. Anticipating the final results of our analyses, the treatment-subgroup interactions are depicted in Figure~\ref{fig:example_glimmertree}, which shows the GLMM tree that accurately recovered the treatment-subgroup interactions.

@@

Although the random-effects part of the GLMM in Equation \ref{eq:mixedeffects} accounts for the nested structure of the dataset, the global fixed-effects part $x_{i}^{\top}\beta$ may not describe the data well. Therefore, we propose the GLMM tree model, in which the fixed-effects part may be partitioned as in Equation \ref{eq:fixedeffects_MOB} while still adjusting for random effects: 
%
\begin{equation}
	\label{eq:glimmertree}
	g(\mu_{i}) = x_{i}^{\top}\beta_{j} + z_{i}^{\top}b
\end{equation}
%
To estimate the parameters of this model, we take an approach similar to that of the mixed-effects regression tree (MERT) approach of \citeA{HajjyBell11} and \citeA{SelaySimo12}. In the MERT approach, the fixed-effects part of a GLMM is replaced by a CART tree with constant fits in the nodes, and the random-effects parameters are estimated as usual. To estimate a MERT, an iterative approach is taken, alternating between (1) assuming random effects known, allowing for estimation of the CART tree, and (2) assuming the CART tree known, allowing for estimation of the random-effects parameters.

@@

\begin{small}
<<eval = FALSE, echo = TRUE>>=
data(a_m_data)
summary(a_m_data)
@
\end{small}

@@

Note that in the example above, the partitioning variables are continuous, but (ordered) categorical partitioning variables may also be specified. Also, we specified only a single variable in the random-effects part, resulting in estimation of a random intercept with respect to \verb|cluster|. More complex random effects can also be specified: for example, specifying the random-effects part as \verb=| (1 + age | cluster) |= would yield a model with a random intercept as well as a random slope for age with respect to cluster. The brackets are necessary to protect the vertical bars in the random effects formulation.

Now, we can use the \verb|plot| method to recreate the tree depicted in Figure \ref{fig:example_glimmertree}:

@@

For MERT, the number of nodes and tree accuracy was not assessed, as the treatment-subgroup interaction design in Figure \ref{fig:modelC} corresponds to a large number of regression tree structures, that would all be different but also correct. Therefore, performance of MERT was only assessed in terms of predictive accuracy.

@@

The predicted treatment-effect differences of LMM tree showed an average correlation of .93 (SD = .13) with the true differences. LM tree and MERT showed lower accuracy, with an average correlations of .88 ($\mathrm{SD}=.19$) and .75 ($\mathrm{SD}=.21$), respectively. The most important predictors of predictive accuracy are depicted in Figure \ref{fig:xyplot_correlations}. Performance of all three algorithms improves with increasing sample size and treatment-effect differences. Furthermore, LMM tree and MERT are not much affected by the presence and magnitude of random effects in the data. LMM tree performs most accurate in most conditions and is never outperformed by the other methods. MERT performs least accurate in most conditions and never outperforms the other methods. The differences in accuracy become less pronounced with larger sample and effect sizes.

@@

For datasets with purely piecewise interactions, the same partition as in Study I (Figure \ref{fig:modelC}) was used. In other words, the outcome variable in this design was calculated as $y_i = x_{i}^{\top}\beta_{j} + z_{i}^{\top}b + \epsilon_i$, with the value of $\beta_j$ depending on the values of $U_2$, $U_1$ and $U_5$.

For the datasets with both piecewise and continuous interactions, the partition as depicted in Figure \ref{fig:modelC} was also used. However, the fixed-effects part $x_{i}^{\top}\beta_{j}$ in each of the terminal nodes now comprised continuous main and (treatment) interaction effects of the partitioning variables. The corresponding node-specific parameters are presented in Table \ref{tab:continuous_terms}. The $\beta_j$ values were chosen to yield the same treatment-subgroup means as in Figure \ref{fig:modelC}. The interaction terms were created using centered $U_k$ variables, calculated by subtracting their variable means.

In datasets with purely continuous interactions, $\beta$ has a global value and no subscript, comprising only purely continuous main and interaction effects, as shown by the single $\beta$ column in Table \ref{tab:continuous_terms}.

\begin{table}[tb!]
\small
\caption{\small Fixed-effects terms in simulations with continuous and combined continuous and piecewise interaction designs.}
\begin{tabular}{lcccccc}
\thickline
Term							&	$\beta_3$&	$\beta_4$&	$\beta_6$&	$\beta_7$&&	$\beta$		\\
\hline
intercept						&	27		&	27		&	27		&	27		&&	27			\\
$U_2$							&	.1		&	.1		&	.1		&	.1		&&	.1			\\
$U_2 \cdot U_1$ 				&	-.357	&	0		&	0		&	0		&&	-.357		\\
$U_2 \cdot U_5$	 				&	0		&	0		&	0		&	.357	&&	.357		\\
$U_2 \cdot U_1 \cdot treatment$	&	-.151	&	0		&	0		&	0		&&	-.151		\\
$U_2 \cdot U_5 \cdot treatment$	&	0		&	0		&	0		&	.151	&&	.151		\\
\hline
\multicolumn{7}{l}{\footnotesize{\textit{Note. }Subscripted $\beta$ values refer to the terminal nodes}}\\	
\multicolumn{7}{l}{\footnotesize in Figure \ref{fig:modelC} for the combined piecewise and continuous}\\
\multicolumn{7}{l}{\footnotesize interaction design; $\beta$ without subscript refers to the global}\\
\multicolumn{7}{l}{\footnotesize coefficients in the continuous interaction design.}\\
\end{tabular}
\label{tab:continuous_terms}
\end{table}

@@

Table \ref{tab:stability} presents statistics on the variables selected for partitioning in subsamples of the dataset. Presence of a comorbid anxiety disorder was selected for partitioning in the majority of LMM trees grown on subsamples of the dataset, while the other variables were selected in at most 4\% of the subsamples. As the comorbid anxiety disorder variable involved only a single splitting value, further assessment of the stability of splitting values was not necessary.

>>>>

\section{Abstract}
Identification of subgroups of patients for which treatment A is more effective than treatment B, and vice versa, is of key importance to the development of personalized medicine. Tree-based algorithms are helpful tools for the  detection of such interactions, but none of the available algorithms allow for taking into account clustered or nested dataset structures, which are particularly common in psychological research. Therefore, we propose the generalized linear mixed-effects model tree (GLMM tree) algorithm, which allows for the detection of treatment-subgroup interactions, while accounting for the clustered structure of a dataset. The algorithm uses model-based recursive partitioning to detect treatment-subgroup interactions, and a GLMM to estimate the random-effects parameters. In a simulation study, GLMM trees show higher accuracy in recovering treatment-subgroup interactions, higher predictive accuracy, and lower Type-II error rates than GLM-based recursive partitioning and mixed-effects regression trees. Also, GLMM tree show somewhat higher predictive accuracy than linear mixed-effects models with pre-specified interaction effect, on average. We illustrate the application of GLMM trees on an individual patient-level data meta-analysis on treatments for depression. We conclude that GLMM trees are a promising exploratory tool for the detection of treatment-subgroup interactions in clustered datasets. An implementation is available in the R package \verb|glmertree| and a short tutorial demonstrating how to fit GLMM trees in practice is provided in the accompanying vignette.\\
\\
\textit{Keywords}: model-based recursive partitioning, treatment-subgroup interactions, random effects, generalized linear mixed-effects model, classification and regression trees

@@

In research on the efficacy of treatments for somatic and psychological disorders, the one-size-fits-all paradigm is slowly losing ground, and personalized or stratified medicine is becoming increasingly important. Stratified medicine presents the challenge of discovering which patients respond best to which treatments. This can be referred to as the detection of treatment-subgroup interactions \cite<e.g., >{DoovyDuss14}. Often, treatment-subgroup interactions are studied using linear models, such as factorial analysis of variance techniques, in which potential moderators have to be specified a-priori, have to be checked one at a time, and continuous moderator variables have to be discretized. This may hamper identification of which treatment works best for whom, especially when there are no a-priori hypotheses about treatment-subgroup interactions. As noted by \citeA{KreayFran06}, there is a need for methods that generate instead of test such hypotheses.

@@

Due to the recursive nature of the splitting, the rectangular regions of the partition can be graphically depicted as nodes in a decision tree, as shown in the artificial example in Figure~\ref{fig:exampletree}. The partition in Figure~\ref{fig:exampletree} is rather simple, based on the values of two predictor variables: duration and anxiety. The resulting tree has a depth of two, as the longest path travels along two splits. Each of the splits in the tree is defined by a splitting variable and value. The first split in the tree separates the observations into two subgroups, based on the splitting variable duration and a splitting value of 8, yielding two rectangular regions, represented by node~2 and node~3. As the observations in node~2 are not further split, node~2 is a terminal node. Node~3 is an inner node, as the observations in this node are further split into nodes~4 and~5, based on the anxiety variable.

If the partition in Figure~\ref{fig:exampletree} would be used for prediction of a new observation, the new observation would be assigned to one of the terminal nodes according to its values on the splitting variables. The prediction is then determined by the distribution of the training observations within the terminal node. For example, the prediction may be the node-specific mean of a single continuous variable. In the current paper, we focus on trees where the terminal nodes consist of a linear (LM) or generalized linear model (GLM), in which case the predicted value for a new observation is determined by the node-specific parameter estimates of the (G)LM, while also adjusting for random effects.

@@

In many instances, researchers may want to detect treatment-subgroup interactions in clustered or nested datasets. For example, in individual-level patient data meta-analyses, where datasets of multiple clinical trials on the same treatments are pooled. In such analyses, the nested or clustered structure of the dataset should be taken into account by including study-specific random effects in the model, prompting the need for a mixed-effects model \cite<e.g., >{CoopyPatt09,HiggyWhit01}. In linear models, ignoring the clustered structure may lead, for example, to biased inference due to underestimated standard errors \cite<e.g., >{BrykyRaud92}. For tree-based methods, ignoring the clustered structure has been found to result in the detection of spurious subgroups and inaccurate predictor variable selection \cite<e.g., >{SelaySimo12, Mart15}. However, none of the purely tree-based methods for treatment-subgroup interaction detection allow for taking into account the clustered structure of a dataset. Therefore, in the current paper, we present a tree-based algorithm which can be used for the detection of interactions and non-linearities in GLMM type models: generalized linear mixed-effects model trees, or GLMM trees.

The GLMM tree algorithm builds on model-based recursive partitioning (MOB, \citeNP{ZeilyHoth08}), which offers a flexible framework for subgroup detection. For example, GLM-based MOB has been applied to detect treatment-subgroup interactions for the treatment of depression \cite{DrieySmit16} and amyotrophic lateral sclerosis \cite{SeibyZeil15}. In contrast to other purely tree-based methods \cite<e.g., >{ZeilyHoth08, SuyTsai09, DussyDoov16}, GLMM tree allows for taking into account the clustered structure of datasets. In contrast to previously suggested regression trees with random effects \cite<e.g., >{HajjyBell11,SelaySimo12}, GLMM trees allow for treatment effect estimation, with continuous as well as non-continuous response variables.

The remainder of this paper is structured into four sections: In the first section, we introduce the GLMM tree algorithm using an artificial motivating dataset with treatment-subgroup interactions. The second section is a short tutorial on how to fit GLMM trees using the R package \verb|glmertree| \readme{still needs to be adapted: vignette}. In the third section, we compare the performance of GLMM trees with that of three other methods: MOB trees without random effects, mixed-effects regression trees (MERTs) and linear mixed-effects models with pre-specified interactions. In the fourth section, we apply a GLMM tree to an existing dataset of a patient-level meta-analysis on the effects of psycho- and pharmacotherapy for depression. In the fith and last section we summarize the results and discuss limitations and directions for future research.

@@

The outcome variable was generated such that there were three subgroups with differential treatment effectiveness, corresponding to the terminal nodes in Figure~\ref{fig:exampletree}: The first subgroup of patients corresponds to node~3 and shows lower post-treatment depression in Treatment~1 than in Treatment~2. The second subgroup of patients corresponds to node~4 and shows about equal post-treatment depression in both treatment conditions. The third subgroup of patients corresponds to node~5 and shows lower post-treatment depression in Treatment~2 than in Treatment~1. Thus, duration and anxiety are true partitioning or moderator variables, whereas age is not. Anticipating the final results of our analyses, the treatment-subgroup interactions are depicted in Figure~\ref{fig:example_glimmertree}, which shows the GLMM tree that accurately recovered the treatment-subgroup interactions.

@@

Although the random-effects part of the GLMM in Equation~\ref{eq:mixedeffects} accounts for the nested structure of the dataset, the global fixed-effects part $x_{i}^{\top}\beta$ may not describe the data well. Therefore, we propose the GLMM tree model, in which the fixed-effects part may be partitioned as in Equation~\ref{eq:fixedeffects_MOB} while still adjusting for random effects: 
%
\begin{equation}
	\label{eq:glimmertree}
	g(\mu_{i}) = x_{i}^{\top}\beta_{j} + z_{i}^{\top}b
\end{equation}
%
To estimate the parameters of this model, we take an approach similar to that of the mixed-effects regression tree (MERT) approach of \citeA{HajjyBell11} and \citeA{SelaySimo12}. In the MERT approach, the fixed-effects part of a GLMM is replaced by a CART tree with constant fits in the nodes, and the random-effects parameters are estimated as usual. To estimate a MERT, an iterative approach is taken, alternating between (1) assuming random effects known, allowing for estimation of the CART tree, and (2) assuming the CART tree known, allowing for estimation of the random-effects parameters.

@@

\begin{small}
<<eval = FALSE, echo = TRUE>>=
data("a_m_data", package = "glmertree")
summary(a_m_data)
@
\end{small}

@@

Note that in the example above, the partitioning variables are continuous, but (ordered) categorical partitioning variables may also be specified. Also, we specified only a single variable in the random-effects part, resulting in estimation of a random intercept with respect to \verb|cluster|. More complex random effects can also be specified: for example, specifying the random-effects part as \verb=... | (1 + age | cluster) | ...= would yield a model with a random intercept as well as a random slope for age with respect to cluster. The brackets are necessary to protect the vertical bars in the random effects formulation.

Now, we can use the \verb|plot| method to recreate the tree depicted in Figure~\ref{fig:example_glimmertree}:

@@

For MERT, the number of nodes and tree accuracy was not assessed, as the treatment-subgroup interaction design in Figure~\ref{fig:modelC} corresponds to a large number of regression tree structures, that would all be different but also correct. Therefore, performance of MERT was only assessed in terms of predictive accuracy.

@@

The predicted treatment-effect differences of LMM tree showed an average correlation of .93 (SD = .13) with the true differences. LM tree and MERT showed lower accuracy, with an average correlations of .88 ($\mathrm{SD}=.19$) and .75 ($\mathrm{SD}=.21$), respectively. The most important predictors of predictive accuracy are depicted in Figure~\ref{fig:xyplot_correlations}. Performance of all three algorithms improves with increasing sample size and treatment-effect differences. Furthermore, LMM tree and MERT are not much affected by the presence and magnitude of random effects in the data. LMM tree performs most accurate in most conditions and is never outperformed by the other methods. MERT performs least accurate in most conditions and never outperforms the other methods. The differences in accuracy become less pronounced with larger sample and effect sizes.

@@

For datasets with purely piecewise interactions, the same partition as in Study I (Figure~\ref{fig:modelC}) was used. In other words, the outcome variable in this design was calculated as $y_i = x_{i}^{\top}\beta_{j} + z_{i}^{\top}b + \epsilon_i$, with the value of $\beta_j$ depending on the values of $U_2$, $U_1$ and $U_5$.

For the datasets with both piecewise and continuous interactions, the partition as depicted in Figure~\ref{fig:modelC} was also used. However, the fixed-effects part $x_{i}^{\top}\beta_{j}$ in each of the terminal nodes now comprised continuous main and (treatment) interaction effects of the partitioning variables. The corresponding node-specific parameters are presented in Table~\ref{tab:continuous_terms}. The $\beta_j$ values were chosen to yield the same treatment-subgroup means as in Figure~\ref{fig:modelC}. The interaction terms were created using centered $U_k$ variables, calculated by subtracting their variable means.

In datasets with purely continuous interactions, $\beta$ has a global value and no subscript, comprising only purely continuous main and interaction effects, as shown by the single $\beta$ column in Table~\ref{tab:continuous_terms}.

\begin{table}[tb!]
\small
\caption{\small Fixed-effects terms in simulations with continuous and combined continuous and piecewise interaction designs.}
\begin{tabular}{lcccccc}
\thickline
Term					&	$\beta_3$&	$\beta_4$		&	$\beta_6$&	$\beta_7$		&&	$\beta$		\\ \hline
intercept				&	27		&	27		&	27		&	27		&&	27		\\
$U_2$					&	.1		&	.1		&	.1		&	.1		&&	.1		\\
$U_2 \cdot U_1$ 			&	$-$.357		&	0		&	0		&	0		&&	$-$.357		\\
$U_2 \cdot U_5$	 			&	0		&	0		&	0		&	.357		&&	.357		\\
$U_2 \cdot U_1 \cdot \mbox{treatment}$	&	$-$.151		&	0		&	0		&	0		&&	$-$.151		\\
$U_2 \cdot U_5 \cdot \mbox{treatment}$	&	0		&	0		&	0		&	.151		&&	.151		\\ \hline
\multicolumn{7}{l}{\footnotesize{\emph{Note:} Subscripted $\beta$ values refer to the terminal nodes}}\\	
\multicolumn{7}{l}{\footnotesize in Figure~\ref{fig:modelC} for the combined piecewise and continuous}\\
\multicolumn{7}{l}{\footnotesize interaction design; $\beta$ without subscript refers to the global}\\
\multicolumn{7}{l}{\footnotesize coefficients in the continuous interaction design.}\\
\end{tabular}
\label{tab:continuous_terms}
\end{table}

@@

Table~\ref{tab:stability} presents statistics on the variables selected for partitioning in subsamples of the dataset. Presence of a comorbid anxiety disorder was selected for partitioning in the majority of LMM trees grown on subsamples of the dataset, while the other variables were selected in at most 4\% of the subsamples. As the comorbid anxiety disorder variable involved only a single splitting value, further assessment of the stability of splitting values was not necessary.
